# Spatial analysis of Hoverfly diversity

```{r setup}
#| echo: false
#| warning: false
#| message: false
#| results: hide
here::i_am("atlas-mnhnl.Rproj")
source(here::here("Atlas", "code", "0_Initialisation.R"))
source(here::here("Atlas", "code", "16_CommunesMap.R"))
source(here::here("Atlas", "code", "17_Effort.R"))
```

## Number of Field Surveys per Grid Cell

```{r}
#| fig-width: 14
#| fig-height: 14
#| fig-align: center
#| echo: false
#| warning: false
#| message: false

carte_effort_cell(effort_cell, rtp, lux_borders, GR2169_c)
```

```{=html}
<div id="img-modal">
  <span class="close-btn" onclick="closeLightbox()">&times;</span>
  <img id="img-modal-content" src="">
</div>

<script>
document.addEventListener("DOMContentLoaded", function() {
  document.querySelectorAll(".lightbox img").forEach(function(img) {
    img.addEventListener("click", function() {
      document.getElementById("img-modal-content").src = this.src;
      document.getElementById("img-modal").classList.add("active");
    });
  });
});

document.addEventListener("click", function(e) {
  if (e.target.id === "img-modal") closeLightbox();
});
document.addEventListener("keydown", function(e) {
  if (e.key === "Escape") closeLightbox();
});

function closeLightbox() {
  document.getElementById("img-modal").classList.remove("active");
}
</script>
```

To account for differences in sampling effort, the two maps below show the average number of records (left) and different species (right) recorded per field survey in each grid cell.

::: {.columns}

::: {.column width="50%"}

## Observations per Survey
::: {.lightbox}

```{r}
#| fig-width: 14
#| fig-height: 14
#| fig-align: center
#| echo: false
#| warning: false
#| message: false
carte_ratio_cell(ratio_cell, rtp, lux_borders, GR2169_c)
```
:::

:::

::: {.column width="50%"}

## Taxa per Survey
::: {.lightbox}

```{r}
#| fig-width: 14
#| fig-height: 14
#| fig-align: center
#| echo: false
#| warning: false
#| message: false
carte_ratio_especes_cell(ratio_especes_cell, rtp, lux_borders, GR2169_c)
```
:::

:::

:::

## Spatial Distribution of Observations
::: {.lightbox}
```{r}
#| fig-width: 14
#| fig-height: 14
#| fig-align: center
#| echo: false
#| warning: false
#| message: false
carte_obs_commune(DB)
```
:::
## Spatial Distribution of Species
::: {.lightbox}
```{r}
#| fig-width: 14
#| fig-height: 14
#| fig-align: center
#| echo: false
#| warning: false
#| message: false
carte_especes_commune(DB)
```
:::


### Author {.author}
 
